Coherent optical association of single molecules

### 2020-09-14 paper.tex
Update on Overleaf.

%% Transfer scheme
After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in figure (). Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time. After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simutaniously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer. 
\todo{clarify coprop of Raman beam?}

>>>>

%% Transfer scheme
After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in figure (). Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time (also minimize source of scattering). After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer. 
\todo{clarify coprop of Raman beam?}
